Fontawesome

### 2022-07-25 Shiny/Test/Fontawesome.Rmd
Adding some more ideas, styling links

>>>>

new icons

[private donations](https://fontawesome.com/icons/wallet?s=solid)

På feks liquid assets/obligations:

[Scale balanced når det er grønt](https://fontawesome.com/icons/scale-balanced?s=solid): fa-solid fa-scale-balanced

[Scale unbalanced når det er rødt](https://fontawesome.com/icons/scale-unbalanced?s=solid)

[På private donations](https://fontawesome.com/icons/chart-line?s=solid)

Andre forslag generelt:

[Globe](https://fontawesome.com/icons/globe?s=solid)

[Magnifying glass + chart](https://fontawesome.com/icons/magnifying-glass-chart?s=solid)

https://fontawesome.com/icons/arrow-up-right-dots?s=solid

https://fontawesome.com/icons/chart-pie?s=solid

https://fontawesome.com/icons/landmark?s=solid

https://fontawesome.com/icons/building-columns?s=solid

https://fontawesome.com/icons/money-bill-trend-up?s=solid

https://fontawesome.com/icons/circle-xmark?s=solid
